Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-08 paper.tex
Fixed label
Figures (no captions)

\subsection{Time based analysis}
\begin{figure}[h]
\centering
\includegraphics[width=8.6cm]{avg-all}
\caption{Distribution of iRail route planning API queries on average per day of the week between October 2012 and December 2015}
\label{fig:average}
\end{figure}

@@

\subsection{Structure of flows in Belgium}

@@

\begin{figure*}
\centering
\includegraphics[width=15cm]{brussels}
\caption{Pair of chord visualization of the city of Brussels: transit flows towards Brussels from elsewhere in Belgium and vice versa.}
\label{fig:brussels}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=15cm]{antwerp}
\caption{Pair of chord visualization of the city of Antwerp: transit flows towards Antwerp from elsewhere in Belgium and vice versa.}
\label{fig:antwerp}
\end{figure*}

\subsection{Counterintuitive results}

>>>>

\subsection{Time Based Analysis}
\begin{figure}[h]
\centering
\includegraphics[width=8.6cm]{avg-all}
\caption{Distribution of iRail route planning API queries on average per day of the week between October 2012 and December 2015}
\label{fig:average}
\end{figure}

@@

\subsection{Structure of Flows in Belgium}

@@

\begin{figure*}
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=13cm]{weekdays_morning.pdf}\\
    \subcaption{Weekdays} % 4 words max
    \label{fig:weekdays_morning}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=13cm]{weekends_morning.pdf}\\
    \subcaption{Weekends} % 4words max
    \label{fig:weekends_morning}
  \end{subfigure}
  \vspace{5.0pt}% To create a bit of vertical space between the 2 figure captions
  \label{fig:mornings}
  \caption{\todo{Needs a caption!}}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{ccc}
  \includegraphics[width=.33\textwidth]{wd-brussels.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-antwerp.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-gent.pdf}\\
  (a) Brussels City&(b) Antwerp City&(c) Gent\\[6pt]
  \includegraphics[width=.33\textwidth]{wd-leuven.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-liege.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-mons.pdf}\\ 
  (d) Leuven&(e) Liege City&(f) Mons\\
\end{tabular}
\label{fig:cities}
\centering
\caption{\todo{Needs a caption!}}
\end{figure*}

\subsection{Counter Intuitive Results}
